---
title       : Slidify Project
author      : Phoebe  
job         : Data Science
framework   : revealjs      # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default       # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
      user: phoebza
      repo: shiny_Project
---

## INTRODUCTION

This presentation addresses the shiny App developed for "Developed Data Product" course project. The peer assessed assignment has two parts:  
* Shiny application and deploy it on Rstudio's servers.  
* Slidify to prepare a reproducible pitch presentation.  
  <br/>
The developed shiny application is avalilable at:

https://phoebza.shinyapps.io/shiny_project/

Source code for ui.R and server.R files are available on the GitHub:

https://github.com/phoebza/slidifyProject

---


## Shiny Apps Features & Functions

The App has inputs on the sidebar panel, & output on main panel.<br/>
Input for the shiny App:
* radiobutton - to choose distribution type to observe
* slider - to control number of observation of dataset generated from radiobutton
* submitButton - to click once all changes have been made (used to not automatically update output)

---


## Shiny Apps Features & Functions (cont.)

Output - TABS:
* distribution fit on histogram graph from generated data from selected distribution type
* histogram graph from generated data from selected distribution type
* summary statistics of generated data
* raw generated data from the selected distribution type from radioButton

--- 

## Data generated for rnorm 

Data generated for normal distribution for 986 observations

```{r , echo=FALSE}
x <- rnorm(986)
x
```

---

## Histogram
 

```{r, echo= FALSE}
set.seed(13489)
hist(x, main = "rnorm histogram")
```
